Software architectures to integrate workflow engines in science gateways

### 2016-05-16 paper.tex
Fixes from @poquirion

The particular case of interaction \texttt{g} (workflow language
conversion) requires particular attention when implementing a real
system since this interaction may not be easily generalizable to any
workflow language. For instance, converting FSL, PSOM or Nipype
pipelines to any other workflow language is problematic because these
engines rely on general-purpose programming languages such as Bash,
Octave and Python, which are much richer than scientific workflow
languages.

>>>>

The particular case of interaction \texttt{g} (workflow language
conversion) requires particular attention when implementing a real
system since this interaction may not be easily generalizable to any
workflow language. For instance, converting FSL, PSOM or Nipype
pipelines to any other workflow language is problematic because these
engines rely on general-purpose programming languages such as Bash,
Octave/Matlab and Python, which are much richer than scientific workflow
languages.
